My Past Work

### 2025-04-23 videos.qmd
Update

>>>>

## Nature Versus Nurture - Podcast Debate in Animation Style

For this project, I focused on experimenting with animation and editing techniques to create a visually engaging, debate-style segment on the topic of transgender athletes in competitive sports. I used Canva for design elements, CapCut for assembling motion sequences, and Final Cut Pro for final compositing and audio syncing.

This was a creative testbed where I explored how layered visuals and stylized transitions could enhance both the clarity and emotional tone of the arguments presented---turning complex social commentary into an accessible and compelling visual narrative.

{{< video https://www.youtube.com/embed/n0J641t6IUE?si=qjfJfLo7WTwzktS1 >}}
